Towards a Cognitive System That Can Recognize Spatial Regions Based on Context

### 2012-01-25 scenarios/cdsr/trunk/papers/AAAI2012/evaluation.tex
klenk's edits done

We evaluated our approach on six classrooms (two simulated and four real) and two simulated studio apartments. The simulated rooms were based on real-life counterparts. For each room we manually encoded the appropriate CDSRs that could be represented by our approach. For the classrooms these were the front and back, and the front and back rows of desks. For the studios these were the kitchen, office and living areas. These manually encoded regions were used as the base CDSRs for analogical transfers, and can be considered the training data for our evaluation.

@@

\subsection{Results}
\begin{table*}
	\center
\begin{tabular}{|c|c|c|}
\hline
Transferred & Manually Encoded & Entire Room \\
\hline
$\bar{p}$=.47 $\sigma$=.37, $\bar{r}$=.46 $\sigma$=.38 & $\bar{p}$=.71 $\sigma$=.30, $\bar{r}$=.67 $\sigma$=.25 & $\bar{p}$=.17 $\sigma$=.11, $\bar{r}$=.98 $\sigma$=.05  \\
\hline
\end{tabular}
\caption{Overall Performance}
  \label{tab:overall}

@@

\begin{table*}
	\center
\begin{tabular}{|c|c|c|c|}
\hline
Region & Inferred & Manually Encoded & Entire Room \\
\hline
Front & $\bar{p}$=.32 $\sigma$=.33, $\bar{r}$=.49 $\sigma$=.41 & $\bar{p}$=.60 $\sigma$=.29, $\bar{r}$=.83 $\sigma$=.19  & $\bar{p}$=.16 $\sigma$=.10, $\bar{r}$=1 $\sigma$=0  \\
\hline
Back & $\bar{p}$=.44 $\sigma$=.37, $\bar{r}$=.56 $\sigma$=.41 & $\bar{p}$=.66 $\sigma$=.25, $\bar{r}$=.84 $\sigma$=.17  & $\bar{p}$=.11 $\sigma$=.06, $\bar{r}$=.99 $\sigma$=.03  \\
\hline
Front Rows & $\bar{p}$=.76 $\sigma$=.27, $\bar{r}$=.28 $\sigma$=.21 & $\bar{p}$=.83 $\sigma$=.31, $\bar{r}$=.50 $\sigma$=.11  & $\bar{p}$=.22 $\sigma$=.08, $\bar{r}$=1 $\sigma$=0  \\
\hline
Back Rows & $\bar{p}$=.72 $\sigma$=.30, $\bar{r}$=.42 $\sigma$=.26 & $\bar{p}$=.80 $\sigma$=.29, $\bar{r}$=.43 $\sigma$=.26  & $\bar{p}$=.19 $\sigma$=.06, $\bar{r}$=1 $\sigma$=0  \\
\hline
Kitchen & $\bar{p}$=.60 $\sigma$=.05, $\bar{r}$=.59 $\sigma$=.34 & $\bar{p}$=.78 $\sigma$=.20, $\bar{r}$=.71 $\sigma$=.13  & $\bar{p}$=.16 $\sigma$=.02, $\bar{r}$=.92 $\sigma$=.13  \\
\hline
Office & $\bar{p}$=.00 $\sigma$=.00, $\bar{r}$=.00 $\sigma$=.00 & $\bar{p}$=.78 $\sigma$=.29, $\bar{r}$=.55 $\sigma$=.20  & $\bar{p}$=.08 $\sigma$=.03, $\bar{r}$=.94 $\sigma$=.06  \\
\hline
Living Room & $\bar{p}$=.40 $\sigma$=.39, $\bar{r}$=.01 $\sigma$=.01 & $\bar{p}$=.63 $\sigma$=.34, $\bar{r}$=.54 $\sigma$=.13  & $\bar{p}$=.35 $\sigma$=.22, $\bar{r}$=.96 $\sigma$=.06  \\
\hline
\end{tabular}
\caption{Performance by Region Type}
  \label{tab:region}	
\end{table*}

>>>>

We evaluated our approach on six classrooms (two simulated and four real) and two simulated studio apartments. The simulated rooms were based on real-life counterparts. For each room we manually encoded appropriate CDSRs that could be represented by our approach. For the classrooms these were the front and back, and the front and back rows of desks. For the studios these were the kitchen, office and living areas. These manually encoded regions were used as the base CDSRs for analogical transfers, and can be considered the training data for our evaluation.

@@

\subsection{Results}
\begin{table*}
	\center
\begin{tabular}{|c|c|c|}
\hline
Transferred & Manually Encoded & Entire Room \\
\hline
$\bar{p}$=.47 $\sigma$=.37, $\bar{r}$=.46 $\sigma$=.38 & $\bar{p}$=.71 $\sigma$=.30, $\bar{r}$=.67 $\sigma$=.25 & $\bar{p}$=.17 $\sigma$=.11, $\bar{r}$=.98 $\sigma$=.05  \\
\hline
\end{tabular}
\caption{Overall Performance Compared Against Target Regions Defined by Three Users}
  \label{tab:overall}

@@

\begin{table*}
	\center
\begin{tabular}{|c|c|c|c|}
\hline
Region & Transferred & Manually Encoded & Entire Room \\
\hline
Front & $\bar{p}$=.32 $\sigma$=.33, $\bar{r}$=.49 $\sigma$=.41 & $\bar{p}$=.60 $\sigma$=.29, $\bar{r}$=.83 $\sigma$=.19  & $\bar{p}$=.16 $\sigma$=.10, $\bar{r}$=1 $\sigma$=0  \\
\hline
Back & $\bar{p}$=.44 $\sigma$=.37, $\bar{r}$=.56 $\sigma$=.41 & $\bar{p}$=.66 $\sigma$=.25, $\bar{r}$=.84 $\sigma$=.17  & $\bar{p}$=.11 $\sigma$=.06, $\bar{r}$=.99 $\sigma$=.03  \\
\hline
Front Rows & $\bar{p}$=.76 $\sigma$=.27, $\bar{r}$=.28 $\sigma$=.21 & $\bar{p}$=.83 $\sigma$=.31, $\bar{r}$=.50 $\sigma$=.11  & $\bar{p}$=.22 $\sigma$=.08, $\bar{r}$=1 $\sigma$=0  \\
\hline
Back Rows & $\bar{p}$=.72 $\sigma$=.30, $\bar{r}$=.42 $\sigma$=.26 & $\bar{p}$=.80 $\sigma$=.29, $\bar{r}$=.43 $\sigma$=.26  & $\bar{p}$=.19 $\sigma$=.06, $\bar{r}$=1 $\sigma$=0  \\
\hline
Kitchen & $\bar{p}$=.60 $\sigma$=.05, $\bar{r}$=.59 $\sigma$=.34 & $\bar{p}$=.78 $\sigma$=.20, $\bar{r}$=.71 $\sigma$=.13  & $\bar{p}$=.16 $\sigma$=.02, $\bar{r}$=.92 $\sigma$=.13  \\
\hline
Office & $\bar{p}$=.00 $\sigma$=.00, $\bar{r}$=.00 $\sigma$=.00 & $\bar{p}$=.78 $\sigma$=.29, $\bar{r}$=.55 $\sigma$=.20  & $\bar{p}$=.08 $\sigma$=.03, $\bar{r}$=.94 $\sigma$=.06  \\
\hline
Living Room & $\bar{p}$=.40 $\sigma$=.39, $\bar{r}$=.01 $\sigma$=.01 & $\bar{p}$=.63 $\sigma$=.34, $\bar{r}$=.54 $\sigma$=.13  & $\bar{p}$=.35 $\sigma$=.22, $\bar{r}$=.96 $\sigma$=.06  \\
\hline
\end{tabular}
\caption{Performance by Region Type}
  \label{tab:region}	
\end{table*}

### 2012-01-25 scenarios/cdsr/trunk/papers/AAAI2012/main-aaai12-cdsr.tex
klenk's edits done

In this paper we presented an integrated cognitive system capable of representing and reasoning about context-dependent spatial regions. The system identifies CDSRs in previously unseen environments through analogy with a single example. This is a difficult cognitive systems task requiring integration of semantic and geometric knowledge to identify regions which can be as small as 8\% of the room. Our system demonstrates a successful integration of a range of technologies including vision, SLAM, qualitative spatial reasoning and analogy to achieve this task. In order to make this rich collection of components work together, our work takes a number of short-cuts that we plan to address with future work. These include a reliance on the initial orientation of a room in a global coordinate frame, the lack of a mechanism to retrieve relevant rooms from memory (e.g. MAC/FAC \cite{forbus/etal1995}), and a lack of transfer post-processing (e.g. comparing the QSRs present in both base and transferred regions) to improve results. In addition, we must complement our system development work with more comprehensive human studies assessing how people define and use these regions as well as how well anchor points capture them. Despite the preliminary nature of this work, our evaluation demonstrates that the system is able to produce CDSRs, which overlap with user-defined region, from a single example for 6 out of 7 region types.

>>>>

In this paper we presented an integrated cognitive system capable of representing and reasoning about context-dependent spatial regions. The system identifies CDSRs in previously unseen environments through analogy with a single example. This is a difficult cognitive systems task requiring integration of semantic and geometric knowledge to identify regions as small as 8\% of the room. Our system demonstrates a successful integration of a range of technologies including vision, SLAM, qualitative spatial reasoning and analogy to achieve this task. In order to make this rich collection of components work together, our work takes a number of short-cuts that we plan to address with future work. These include a reliance on the initial orientation of a room in a global coordinate frame, the lack of a mechanism to retrieve relevant rooms from memory (e.g. MAC/FAC \cite{forbus/etal1995}), and a lack of transfer post-processing (e.g. comparing the QSRs present in both base and transferred regions) to improve results. In addition, we must complement our system development work with more comprehensive human studies assessing how people define and use these regions as well as how well anchor points capture them. Despite the preliminary nature of this work, our evaluation demonstrates that the system is able to transfer CDSRs that overlap with user-defined regions for 6 out of 7 region types.
